On the Functionality of the Multilayer Perceptron

### 2020-10-20 Thesis/Drafts/Buell-PHYS799-ThesisDraft0.tex
Updates to Thesis Draft 0

@@

\paragraph*{}Consider the biological process of hearing a sound wave and matching it to a source. We can model this behavior by some unknown function $F$. We produce an approximation of that function $F^*$ that can map the contents of a sound file that have been generated by a chaotic synthesizer to a potential source. For a set of inputs $\vec{x} = \big\{ x_0 , x_1 , x_2 , ... , x_{p-1} \big\}$ and a set of classes $0$ through $k-1$, we denote this function as:
\begin{equation}
\label{eqn-MappingFunction}
F^*: \vec{x} \rightarrow \big\{ 0 , 1 , 2 , ... , k-1 \big\}
\end{equation}

\paragraph*{}In secs. (\ref{subsec-NerualNetworkIntro}) and (\ref{subsec-NetworkStructure}), we introduce the nature and structure of a neural network and how it can use used in part to solve this problem. We show it's mathematical function analogue and how

@@

\paragraph*{}The task of algorithmically matching sound files to musical instrument classes in exceedingly difficult through conventional computer programming techniques. Because of the complexity of sound waves, brain's interpretation them, the challenge arises as to how to build some sort of program that could function at a level above general procedural or explicit instructional rules. Rather than \textit{hard-coding} a set of conditions or parameters for a classification program, we seek an architecture that allows for a computer to \textit{learn} and change and update itself as it is presented with more data. Such an algorithm exists in the form of a \textit{Neural Network} \cite{Geron2,Goodfellow,Levine}.

\paragraph*{}A neural network is a mathematical function that seeks to produce an approximation $F^*$, of some usually unknown function $F$ . For audio recognition, $F$ is some function, or series of functions, that occurs in the brain which allows for a listener to take the sensation of audio, and map it to a known musical instrument. For a neural network, a model must construct an approximate function $F^*$ using a set of parameters $\Theta$, which allows the model to map a series of inputs, $x$ (called \textit{features}) to a series of outputs, $y$ (called \textit{predictions}) \cite{Goodfellow,James,Virtanen}.

@@

\paragraph*{}Over the course of their lives, humans will learn to map sounds to sources almost effortlessly. Given an example, and the appropriate label, humans can do this with very reasonable accuracy over a wide array of sounds \cite{Olsen,White}. We can simplify the idea of humans recognizing sound as some function or operation that occurs within the brain, accepting an input sound, and produces an output label. Similarly, a neural network can be constructed, presented with \textit{features} of multiple, labeled sound waves and learns a set of parameters $\Theta$ that allows for the mapping to a source.

@@

@@

\paragraph*{}Audio and Machine learning researchers M. Kashif Saeed Khan and Wasfi G. Al-Khatib discuss the vitality of feature selection \cite{Khan}: \textcolor{red}{I'm not sure how to introduce the importance of feature extraction}
\begin{quote}
The data reduction stage which is also called feature extraction, consists of discovering a few important facts about each class. The choice of features is critical as it greatly affects the accuracy of audio classification. 
\end{quote}
In order to properly train a neural network, the model must be presented with an appropriate set of training input $x$ and a complementary set of training labels $y$ \cite{Geron,Goodfellow,James}. It becomes quickly apparent that the nature of information contained in the input object $x$, called \textit{features}, is \textit{extremely important} to the performance of the classifier. Consider the task of identifying cats and dogs from images, given only images consisting of the top-most row of pixels. The inappropriate choice features does not reflect the significant characteristics of the signal.

\paragraph*{}Tuomas Virtanen, machine learning and audio engineer writes in his book, "Computational Analysis of Sound Scene and Events" about specifically how features must be chosen \cite{Virtanen}:
\begin{quote}
For recognition algorithms, the necessary property of the acoustic features is low variability among features extracted from examples assigned to the same class, and at the same time high variability allowing distinction between features extracted from examples assigned to different classes.
\end{quote}
In constructing a neural network classifier, the development of appropriate features is of the utmost importance. To ensure the construction of a suitable model, we derive features based from three sources (i) a spectrogram matrix of the waveform, (ii) the time-space representation of the waveform, and (iii) the frequency-space representation of the waveform. It is important to note that although this algorithm will classify sound waves to instruments, the model will never actually be presented with a waveform directly, instead it will rely solely these features.

\paragraph*{}Once we produce an sufficient set of features, we concatenate them into a single object, $\hat{x}$, called the \textit{feature-vector} \cite{Goodfellow}. In the training process this object, along with the appropriate classification label, $y$ is presented to the neural network for processing. This process of constructing a feature vector from any data set is vital and is used to represent the data set in a far more compact and non-redundant format \cite{Virtanen,Liu}

\paragraph*{}To ensure suitable performance of this sound wave classification neural network, a great deal of time has been devoted to the construction of the elements of the feature vector. These features are derived are principles of music, digital signal processing, previous work success, and most importantly physics. In the following sections, we outline the set of $21$ features used in the classification process

@@

\paragraph*{}The $21$ features are from each file are organized into one of two array structures. each called a \textit{design matrix}. A design matrix is an N-Dimensional array of real floating-point numbers that stores the features in a convenient way for the neural network to digest. For this hybrid neural-network, we use two matrices, $X_1$ and $X_2$, each containing data from $b$ audio file samples. each has shape given by:
\begin{equation}
\label{eqn-X1Shape}
X_1 \in \mathbb{R}^{(b \times N' \times k \times 1)}
\end{equation}
\begin{equation}
\label{eqn-X2Shape}
X_2 \in \mathbb{R}^{(b \times P)}
\end{equation}
Where $Q' \times R' \times 1$ gives the shape of a single spectrogram matrix $S$, described in sect. (\ref{subsec-spectrogram}). Similarly, $P$ is the number of features derived from the time and frequency-representation of features outlined in sec. (\ref{subsec-time}) and sec.(\ref{subsec-frequency}).The first axis, with size $b$ indicates that there are $b$ samples stored in that design matrix.
A row of $X_2$ has shape $1 \times P$ where there are $P$ features within the \textit{feature-vector} for each sample. Matrix $X_1$ is presented to the convolutional branch of the network to be process as an a collection of images, and matrix $X_2$ is presented to the perceptron branch to be processed as a collection of vectors.

@@

\paragraph*{}Preprocessing a data set is a necessary step to execute prior to feature extraction \cite{Geron2,James}. In the case of audio files, preprocessing usually consists of ensuring that the data set contains the following:
\begin{enumerate}
\item A suitably sized number of files, of reasonable audio quality, with normalized amplitudes
\item Audio encoded in a standard, and consistent format
\item A consistent sample rate and bit depth between audio files
\item A consistent number of channels
\end{enumerate}
Note that different projects may require a different set of requirement from preprocessing \cite{Virtanen}. For this project, we have chosen to use the following parameters:
\begin{enumerate}
\item Roughly $4000$ audio files Professionally or semi-professionally recorded in a studio. \textcolor{red}{Citation needed!}. All ampltiudes have been normalized to $\pm 1$ unit.
\item All audio has be converted into \textit{.WAV} files from other formats, such as \textit{.AIF} or \textit{.MP3} using a MATLAB program
\item All audio is sampled at $44,100$ Hz and \textcolor{blue}{Bit depth needed - 16? 24?}
\item All audio has been down-mixed into mono-channel waveforms.
\end{enumerate}

@@

\paragraph*{}A spectrogram is produced by the method of \textit{frame-blocking}, which is very prevalent in audio signal classification. Frame-blocking takes a raw waveform or signal, $s$ and decomposes it into a set of analysis frames, $a_i$, with each being $N$ samples in length, and has a fixed overlap with the next adjacent frame. Each of the $k$ frames then allows for a section of the signal in somewhat stationary state \cite{Liu,Zhang,Kahn,Virtanen}. For this project, we have chosen to use frames of size $N = 4096$ with a $75\%$ or $3072$ sample overlap. We also choose to use exactly $k = 256$ frames. Waveforms that are too short are padded with zeros, and waveforms that are too long are truncated. The audio has been sampled at $f_s = 44100$ samples/second, so ach frame represents a slice of time that is about $0.1$ seconds long.

\paragraph*{}We concatenate each analysis frame, $a_{i}, i \in [0,k-1]$ into a single $k \times N$ matrix, called $A$. Each row is a frame, each column is an index in that frame
\begin{equation}
\label{eqn-FrameMatrix}
A = \big\{ a_{0} , a_{1} , a_{2} , ... , a_{k-1} \big\} = 
\begin{bmatrix}
a_{0}[0] & a_{0}[1] & a_{0}[2] & \hdots & a_{0}[N-1] \\
a_{1}[0] & a_{1}[1] & a_{1}[2] & \hdots & a_{1}[N-1] \\
a_{2}[0] & a_{2}[1] & a_{2}[2] & \hdots & a_{2}[N-1] \\
\vdots 		& \vdots 	  & \vdots 		& \ddots & \vdots        \\
a_{k-1}[0] & a_{k-1}[1] & a_{k-1}[2] & \hdots & a_{k-1}[N-1] \\
\end{bmatrix}
\end{equation}
We use bracket notation, $[j]$ to indicate that each analysis frame $a_i$ is array-like. Many programming languages could also use the following indexing conventions for matrix $A$:
\begin{equation}
\label{eqn-IndexingA}
A_{i,j} = A_i[j] = A[i][j] = A[i,j]
\end{equation}
These all represent equivalent entries.

\paragraph*{}After frame-blocking, we apply a \textit{windowing function} to each frame. A standard \textit{Hann Window} of $N$ samples is generated as a $1 \times N$ row-array, $H$. The $n$-th index in a Hann window with $N$ samples is defined:
\begin{equation}
\label{eqn-Hann}
H[n] = \frac{1}{2}\bigg[ 1 - \cos\Big( \frac{2\pi n}{N-1}\Big)\bigg]
\end{equation}
This window function is applied to each analysis frame by computing the element-wise product of the Hann window array, $H$ and each row of the analysis frames matrix, $A_{i,:}$. Result is an $k \times N$ array, $\widetilde{A}$:
\begin{equation}
\label{eqn-WindowMatrix}
\widetilde{A_i} = A_i \odot H
\end{equation}
The window function allows for a cleaner transform into frequency space \cite{Virtanen}.

\paragraph*{}Finally, we perform a \textit{Discrete Fourier Transform} (DFT) to bring each analysis frame from a time domain into a frequency domain \cite{Olson,Peatross}. The Discrete Fourier Transform is applied by producing an $N \times N$ \textit{transform matrix}, often noted at $\mathbb{W}$. Let $\omega^k = e^{\frac{-2\pi i}{N}k}$, then the DFT matrix for a time-space containing $N$ samples
\begin{equation}
\label{eqn-DFTMatrix}
\mathbb{W} = \frac{1}{\sqrt{N}}
\begin{bmatrix}
1 & 1 & 1 & 1 & \hdots & 1 \\
1 & \omega		& \omega^2 & \omega^3 & \hdots & \omega^{N-1} \\
1 & \omega^2	& \omega^4 & \omega^6 & \hdots & \omega^{2(N-1)} \\
1 & \omega^3	& \omega^6 & \omega^9 & \hdots & \omega^{3(N-1)} \\
\vdots & \vdots & \vdots & \vdots & \ddots & \vdots \\
1 & \omega^{N-1} & \omega^{2(N-1)} & \omega^{3(N-1)} & \hdots & \omega^{(N-1)^2}
\end{bmatrix}
\end{equation}
Each column of the matrix is a complex sinusoidal oscillating with an integer number of periods within the $N$-sample length window \cite{Short,Peatross}.The DFT is applied by a taking the matrix -product of $\mathbb{W}$ and $\widetilde{A}^T$. The transpose of $\widetilde{A}$ then makes each analysis frame into a column vector, which gives the appropriate dimension for multiplication.
\begin{equation}
\label{eqn-DFT}
\text{DFT}\big[ \widetilde{A} \big] = \mathbb{W}\widetilde{A}^T
\end{equation}

@@

\paragraph*{}Each column of the $S$ matrix is now a single-frame that has been moved into a frequency-space representation, thus there are $k$ columns, just as there were $k$ time-series analysis frames. Given the discretized nature of digital audio, the frequency-space representation is not a continuous function, but rather a column vector, where the frequency has been assigned to one of $N$ bins, ranging from $-f_s / 2$ to $+f_s/2$.

\paragraph*{}Standard western musical instruments seldom extend above $6$ kHz \cite{Olson,Virtanen,White}. This means that when constructing the spectrogram, we will rarely ever see energy present above this frequency at any time, and the $S$ matrix will contain mostly zero, or zero-like entries. As a result of this, we can simply crop each matrix to only represent frequencies that are only between $0$ Hz and $6000$ Hz. This makes the input array smaller, and eliminates redundant and non-useful information. The number rows in the $S$ matrix is reduced from $N$ down to $N'$.

\paragraph*{}Each spectrogram is now $N' \times k \times 1$ ($1$ representing a single gray-scale pixel channel, as opposed to $3$ channels for RGB inputs) and effectively encodes the energy distribution of the waveform as a function of both time and frequency. The spectrogram is the first feature used in this model. For this classifier, we have chosen $N' = 558$ and $k = 256$. For training, a batch of $b$ samples are concatenated into a single array object. \textcolor{blue}{See Neural Network section for more details}. For a batch of $b$ samples of $N' \times k \times 1$ spectrograms, we shape $X_1$ such that:
\begin{equation}
\label{eqn-X1 shape}
X_1 = \big\{ S^{(0)},S^{(1)},S^{(2)}, ... , S^{(b-1)} \big\} \in \mathbb{R}^{(b \times N' \times k \times 1)}
\end{equation}
Which is consistent with the shape of the $X_1$ matrix outlined in eqn(\ref{eqn-X1Shape}). This matrix is presented to the \textit{Convolution} branch of the neural network for processing. \textcolor{blue}{See Neural Network section for more details}

>>>>

\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\lhead{Landon Buell}
\rhead{B.S. Physics Thesis}
\cfoot{\thepage}

@@

\paragraph*{}Consider the biological process of hearing a sound wave and matching it to a source. We can model this behavior by some unknown function $F$ and approximate it with the function $F^*$. This can map the contents of a sound file to a potential source as to mimic $F$. For a set of inputs (called features or predictors) $\vec{x} = \big\{ x_0 , x_1 , x_2 , ... , x_{p-1} \big\}$ and a set of classes $0$ through $k-1$, we denote this function as:
\begin{equation}
\label{eqn-MappingFunction}
F^*: \vec{x} \rightarrow \big\{ 0 , 1 , 2 , ... , k-1 \big\}
\end{equation}

\paragraph*{}In secs. (\ref{subsec-NerualNetworkIntro}) and (\ref{subsec-NetworkStructure}), we introduce the nature and structure of a neural network and how it can use used in part to solve this problem.

@@

\paragraph*{}The task of algorithmically matching sound files to musical instrument classes in exceedingly difficult through conventional computer programming techniques. Because of the complexity of sound waves, and the brain's interpretation of them, the challenge arises as to how to build some sort of program that could function at a level above general procedural or explicit instructional rules. Rather than \textit{hard-coding} a set of conditions or parameters for a classification program, we seek an solution that allows for a computer to \textit{learn} from past examples in order change and update itself. Such an algorithm exists in the form of a \textit{Neural Network} \cite{Geron2,Goodfellow,Levine}.

@@

\paragraph*{}A neural network is a mathematical function that seeks to produce an approximation $F^*$, of some usually unknown function $F$ . For audio recognition, $F$ is some function or series of functions that occurs in the brain which allows for a listener to process the sensation of audio, and map it to a known source object. For a neural network, function $F^*$ uses a set of parameters $\Theta$, to map a series of inputs, $x$ (called \textit{features}) to a series of outputs, $y$ (called \textit{predictions}) \cite{Goodfellow,James,Virtanen}.

\paragraph*{}Over the course of their lives, humans will learn to map sounds to sources almost effortlessly \cite{Virtanen}. Given an example, and the appropriate label, humans can do this with very reasonable accuracy over a wide array of sounds \cite{Olsen,White}. We can simplify the idea of humans recognizing sound as some function or operation that occurs within the brain, accepting an input sound, and produces an output label. Similarly, a neural network can be constructed, presented with \textit{features} of multiple, labeled sound waves and learns a set of parameters $\Theta$ that allows for the mapping to a source.

@@

\newpage
\section{Properties of Musical Instruments}
\label{sec-Instruments}

\textcolor{red}{I have notes written out for this section, I just need to write it out here soon}

@@

\paragraph*{}Audio machine learning researchers M. Kashif Saeed Khan and Wasfi G. Al-Khatib discuss the vitality of feature selection \cite{Khan}: \textcolor{red}{I'm not sure how to introduce the importance of feature extraction}
\begin{quote}
The data reduction stage which is also called feature extraction, consists of discovering a few important facts about each class. The choice of features is critical as it greatly affects the accuracy of audio classification. 
\end{quote}
In the case of the biological process, the features of the audio is simply the raw time series waveform as processed by the brain. This information is then used into categorize the source. In the case of the neural network model, the time series waveform alone has shown to be unreliable in classification tasks \cite{Virtanen}. We must then develop a set of features or predictors that can describe important properties of the waveform in a far more efficient manner \cite{Goodfellow,James}.

\paragraph*{}It becomes quickly apparent that the choice of features is extrodinarily important to the process of training and evaluation of the classifier model. Consider the task of identifying cats and dogs from images, given only images consisting of the top-most row of pixels. The inappropriate choice features does not reflect the significant characteristics of the data.

\paragraph*{}Tuomas Virtanen, machine learning and audio engineer writes in his book, "Computational Analysis of Sound Scene and Events" about specifically how features must be chosen \cite{Virtanen}:
\begin{quote}
For recognition algorithms, the necessary property of the acoustic features is low variability among features extracted from examples assigned to the same class, and at the same time high variability allowing distinction between features extracted from examples assigned to different classes.
\end{quote}
To ensure the construction of a suitable model, we derive features based from three representations of the audio file: (i) a spectrogram matrix of the waveform, (ii) the time-space representation of the waveform, and (iii) the frequency-space representation of the waveform. It is important to note that although this algorithm will classify sound data to instruments, the model will never actually be presented with a waveform directly, instead it will rely solely on the features.

\paragraph*{}Once we produce an sufficient set of features, we concatenate them into a single object, $\hat{x}$, called the \textit{feature-vector} \cite{Goodfellow}. In the training process this object, along with the appropriate classification label, $y$ is presented to the neural network for processing. This process of constructing a feature vector from any data set is vital and is used to represent the data set in a far more compact and non-redundant format \cite{Virtanen,Liu,Kahn}.

\paragraph*{}To ensure suitable performance of this sound wave classification neural network, a great deal of time has been devoted to the construction of the elements of the feature vector. These features are derived are principles of music, digital signal processing, previous work, and underlying physics that governs the behavior of instruments. In the following sections, we outline the set of $21$ features used in the classification process

@@

\paragraph*{}The $21$ features are from each file are organized into one of two array structures. each called a \textit{design matrix}. A design matrix is an N-Dimensional array of real floating-point numbers that stores the features in a convenient way for the neural network to digest. For this hybrid neural-network, we use two matrices, $X_1$ and $X_2$, each containing data from $b$ audio file samples. each has shape given by:
\begin{equation}
\label{eqn-X1Shape}
X_1 \in \mathbb{R}^{(b \times N' \times k \times 1)}
\end{equation}
\begin{equation}
\label{eqn-X2Shape}
X_2 \in \mathbb{R}^{(b \times p)}
\end{equation}
Where $Q' \times R' \times 1$ gives the shape of a single spectrogram matrix $S$, described in sect. (\ref{subsec-spectrogram}). Similarly, $p$ is the number of features derived from the time and frequency-representation of features outlined in sec. (\ref{subsec-time}) and sec.(\ref{subsec-frequency}).The first axis, with size $b$ indicates that there are $b$ audio samples stored in that design matrix.

@@

\paragraph*{}Preprocessing a data set is a necessary step to execute prior to feature extraction \cite{Geron2,James}. In the case of audio files, preprocessing usually consists of ensuring that the data set contains the following:
\begin{enumerate}
\item A suitably sized number of files, of reasonable audio quality, with normalized amplitudes
\item Audio encoded in a standard, and consistent format
\item A consistent sample rate and bit depth between audio files
\item A consistent number of channels
\end{enumerate}
Note that different projects may require a different set of requirement from preprocessing \cite{Virtanen}. For this project, we have chosen to use the following parameters:
\begin{enumerate}
\item Roughly $16,000$ audio files Professionally or semi-professionally recorded in a studio. \textcolor{red}{Citation needed!}. All ampltiudes have been normalized to $\pm 1$ unit.
\item All audio has be converted into \textit{.WAV} files from other formats, such as \textit{.AIF} or \textit{.MP3} using a MATLAB program
\item All audio is sampled at $44,100$ Hz and \textcolor{blue}{Bit depth needed - 16? 24?}
\item All audio has been down-mixed into mono-channel waveforms.
\end{enumerate}

@@

\paragraph*{}A spectrogram is produced by the method of \textit{frame-blocking}, which is very prevalent in audio signal classification \cite{Liu,Zhang}. Frame-blocking takes a raw waveform or signal, $s$ and decomposes it into a set of analysis frames, $a_i$, with each being $N$ samples in length, and has a fixed overlap with the next adjacent frame. Each of the $k$ frames then allows for a section of the signal in somewhat stationary state \cite{Kahn,Virtanen}.

\paragraph*{}For this project, we have chosen to use frames of size $N = 4096$ with a $75\%$ or $3072$ sample overlap. Since each audio file contains a different number of samples, we choose the number of frames, $k$ to be less than or equal to $256$. If $k > 256$, the waveform in truncated, if $k \leq 256$ the frames left as is. The audio has been sampled at $f_s = 44100$ samples/second, so each frame represents a slice of time that is about $0.1$ seconds long.

\paragraph*{}We concatenate each analysis frame, $a_{i}, i \in [0,k-1]$ into a single $k \times N$ matrix, called $A$. Each row is a frame, each column is an index in that frame
\begin{equation}
\label{eqn-FrameMatrix}
A = \big\{ a_{0} , a_{1} , a_{2} , ... , a_{k-1} \big\} = 
\begin{bmatrix}
a_{0}[0] & a_{0}[1] & a_{0}[2] & \hdots & a_{0}[N-1] \\
a_{1}[0] & a_{1}[1] & a_{1}[2] & \hdots & a_{1}[N-1] \\
a_{2}[0] & a_{2}[1] & a_{2}[2] & \hdots & a_{2}[N-1] \\
\vdots 		& \vdots 	  & \vdots 		& \ddots & \vdots        \\
a_{k-1}[0] & a_{k-1}[1] & a_{k-1}[2] & \hdots & a_{k-1}[N-1] \\
\end{bmatrix}
\end{equation}
We use bracket notation, $a[j]$ to indicate that each analysis frame $a_i$ is array-like. The following indexing conventions for matrix $A$ all represent the same entry:
\begin{equation}
\label{eqn-IndexingA}
A_{i,j} = A_i[j] = A[i][j] = A[i,j]
\end{equation}

\paragraph*{}After frame-blocking, we apply a \textit{windowing function} to each frame. A standard \textit{Hann Window} of $N$ samples is generated as a $1 \times N$ row-array, $H$. The $n$-th index in a Hann window with $N$ samples is defined:
\begin{equation}
\label{eqn-Hann}
H[n] = \frac{1}{2}\bigg[ 1 - \cos\Big( \frac{2\pi n}{N-1}\Big)\bigg]
\end{equation}
This window function is applied to each analysis frame by computing the element-wise product of the Hann window array, $H$ and each row of the analysis frames matrix, $A_{i,:}$. Result is an $k \times N$ array, $\widetilde{A}$:
\begin{equation}
\label{eqn-WindowMatrix}
\widetilde{A_i} = A_i \odot H
\end{equation}
The window function allows for a cleaner transform into frequency space \cite{Virtanen}. \textcolor{blue}{Expand on this. HOW? Why do we use a windowing function?}

\paragraph*{}Finally, we perform a \textit{Discrete Fourier Transform} (DFT) to bring each analysis frame from a time domain into a frequency domain \cite{Olson,Peatross}. The Discrete Fourier Transform is applied by producing an $N \times N$ \textit{transform matrix}, often noted at $\mathbb{W}$. Let $\omega^k = e^{\frac{-2\pi i}{N}k}$, then the DFT matrix for a time-space containing $N$ samples
\begin{equation}
\label{eqn-DFTMatrix}
\mathbb{W} = \frac{1}{\sqrt{N}}
\begin{bmatrix}
1 & 1 & 1 & 1 & \hdots & 1 \\
1 & \omega		& \omega^2 & \omega^3 & \hdots & \omega^{N-1} \\
1 & \omega^2	& \omega^4 & \omega^6 & \hdots & \omega^{2(N-1)} \\
1 & \omega^3	& \omega^6 & \omega^9 & \hdots & \omega^{3(N-1)} \\
\vdots & \vdots & \vdots & \vdots & \ddots & \vdots \\
1 & \omega^{N-1} & \omega^{2(N-1)} & \omega^{3(N-1)} & \hdots & \omega^{(N-1)^2}
\end{bmatrix}
\end{equation}
Each column of the matrix is a complex sinusoidal oscillating with an integer number of periods within the $N$-sample length window \cite{Short,Peatross}.The DFT is applied by a taking the matrix - product of $\mathbb{W}$ and $\widetilde{A}^T$. The transpose of $\widetilde{A}$ then makes each analysis frame into a column vector, which gives the appropriate dimension for multiplication.
\begin{equation}
\label{eqn-DFT}
\text{DFT}\big[ \widetilde{A} \big] = \mathbb{W}\widetilde{A}^T
\end{equation}

@@

\paragraph*{}Each column of the $S$ matrix is now a single-frame that has been moved into a frequency-space representation, thus there are $k$ columns, just as there were $k$ time-series analysis frames. Given the discretized nature of digital audio, the frequency-space representation is not a continuous function, but rather a column vector, where the frequency has been assigned to one of $N$ bins, ranging from $-f_s / 2$ to $+f_s/2$. To ensure homogeneous input sizes between all samples, we zero-pad the matrix $S$ with additional columns until $k = 256$. Recall that wave forms were truncated to ensure that $k \leq 256$ analysis frames.

\paragraph*{}Standard western musical instruments seldom extend above $6$ kHz \cite{Olson,Virtanen,White}. This means that when constructing the spectrogram, we will rarely ever see energy present above this frequency at any time, and the $S$ matrix will contain mostly zero, or zero-like entries. To condense the size of the matrix, we select onlt the frequency bins that correspond to energies between $0$ Hz and $6000$ Hz. This makes the input array smaller, and eliminates redundant and non-useful information. The number rows in the $S$ matrix is reduced from $N$ down to $N'$.

\paragraph*{}Each spectrogram is now $N' \times k \times 1$ (The last axis represents a single pixel channel, as opposed to $3$ channels for RGB inputs, etc.) and effectively encodes the energy distribution of the waveform as a function of both time and frequency. The spectrogram is the first feature used in this model. For this classifier, we have chosen $N' = 558$ and $k = 256$. For training, a batch of $b$ samples are concatenated into a single array object. For a batch of $b$ samples of $N' \times k \times 1$ spectrograms, we shape $X_1$ such that:
\begin{equation}
\label{eqn-X1 shape}
X_1 = \big\{ S^{(0)},S^{(1)},S^{(2)}, ... , S^{(b-1)} \big\} \in \mathbb{R}^{(b \times N' \times k \times 1)}
\end{equation}
Which is consistent with the shape of the $X_1$ matrix outlined in eqn(\ref{eqn-X1Shape}). This matrix is presented to the \textit{Convolution} branch of the neural network for processing.
